---
title: "Simple document"
output: html_document
---

I'm an R Markdown document! 

# Section 1

Here's section 1

##Section 1.1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

```{r}
mean(samp)
```

# Testing a dataframe 


Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?
```{r random}
library(tidyverse)

la_df = tibble(
sample = rnorm(500, 1),
new = sample > 0,
new_abs = abs(sample)
)

ggplot(la_df, aes(x = new_abs)) + geom_histogram()
```
